\speculake: Hiding Malware in Speculative Execution

### 2018-05-09 paper/abstract.tex

We introduce \emph{\speculake}, which compiles arbitrary malicious code into a
seemingly-benign payload binary. When a separate trigger program runs on the same
machine, it mistrains the CPU's branch predictor, causing the payload program to
\emph{speculatively} execute code, and communicating its results back to the
rest of the payload program, changing its behavior.

>>>>

We introduce \emph{\speculake}\footnote{Executable Spectre}, which compiles
arbitrary malicious code into a seemingly-benign payload binary. When a separate
trigger program runs on the same machine, it mistrains the CPU's branch
predictor, causing the payload program to \emph{speculatively} execute code, and
communicating its results back to the rest of the payload program, changing its
behavior.
